Ear canal dynamic motion piezoelectric energy harvester using a bistable resonator cycled by coupled hydraulic switches made of collapsed flexible tubes.

### 2022-10-20 article_system.tex
update revisions_FF part1

		BB                       & Buckled blade                                           \\

@@

		GB                       & Guide blade                                             \\

@@

Based on the analysis of the literature, we propose a new solution optimizing the energy conversion efficiency to maximize the harvested energy from the ear canal dynamic motion. The next section states on the hydraulic energy source characterization and on the harvesting strategy that we adopted. Section \ref{sec:HARVESTER PRESENTATION AND OPERATION PRINCIPLE} presents the harvester and describes its operation principle. Section \ref{sec:SYSTEM MODELING} details the global system modeling and section \ref{sec:NUMERICAL MODEL AND SIMULATIONS} presents the numerical simulation of the theoretical behavior of the harvester. Then section \ref{sec:EXPERIMENTAL CHARACTERIZATIONS OF THE ELECTROMECHANICAL CONVERTER} then exposes the experimental validation performed on the electromechanical converter stage and section \ref{sec:EXPERIMENTAL APPROACH FOR THE HV DESIGN} shows the experimental approach for the design of the hydraulic valves for the system cycling. Then, section \ref{sec:MODEL RECALIBRATION WITH EXPERIMENTAL DATA} presents the experimentally adjusted global harvester model and discusses this work major contributions and the harvester potential. Finally, a conclusion is stated in the last section.

@@

    %///////////////////////////////////////////// 
	\subsection{The harvesting strategy}	
	\label{The harvesting strategy}
    %/////////////////////////////////////////////
Electromagnetic transducers are usually used to harvest energy from kinetic (vibration) energy sources. In fact, the power density of electromagnetic transducers decreases as much as the effective volume of transducing material and the frequency of the energy source decrease \cite{Priya2017,Kulah2008}. Also, the fabrication and the integration of the coil and the moving magnet can come out to be difficult as the gap between the two components has to be carefully managed to prevent non-linear unpredicted responses \cite{Caruntu2001}. Thus, piezoelectric ceramics appear like good candidates, but they can not be easily used because of their high stiffness and their high resonance frequencies (>$1.57$Hz). Therefore, the harvesting system could benefit from a frequency-up conversion stage \cite{Ashraf2011,Peng2021} to increase the frequency of the energy source and so the energy conversion efficiency of piezoelectric ceramic transducers. A majority of the frequency-up systems with piezoelectric transducers use mechanical stops with piezoelectric ceramic cantilevers to reach high frequencies with a good mechanical coupling \cite{Edwards2013,Gu2011,Lee2007}. Stoppers however dissipate energy. Alternative solutions use mechanically bistable resonators (BR) to perform frequency-up \cite{Vocca2012}. Recent works led to the development and optimization of  bistable structures integrating stacked piezoelectric ceramics inside flextensional elastic structures \cite{Huguet2017}. They show enhanced performances due to high electromechanical coupling.

We can estimate the best choice maximizing the energy extraction from the hydraulic source. To be harvested, the energy has to be stored in a mechanical potential reservoir at first, to be then converted in electricity by the transducer. The hydraulic-mechanic interface can be a hydraulic cylinder (HC). It could store then the energy in the frequency-up converter by actuating it at the frequency of human mastication. Figure \ref{fig:hydraulic_mechanic_interface} schematizes the mechanical interaction between the HC and the resonator assimilated to a spring of stiffness $K_s$. During the low frequency actuation, the forces applied on each side of the HC piston are equal. Equation \ref{eq:hydraulic-mechanic_interface} models the hydraulic-mechanic interface with $x_{m}$ and $ S_{hc}$ being respectively the dynamic mass position on the $\vec{x}$ axis and the HC internal section.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{equation}
	\Delta p_{ear}\ S_{hc} = K_{s}\ x_{m}
	\label{eq:hydraulic-mechanic_interface}
\end{equation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={19.7cm 0cm 0cm 13cm},clip, width=0.7\linewidth]{figures/hydraulic_mechanic_interface.pdf}
	\caption{Hydraulic source exploitation depending on the mechanical load}
	\label{fig:hydraulic_mechanic_interface}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Therefore, the potential energy stored in a linear resonator from the ideal hydraulic source previously described can be expressed as follows :
\begin{equation}
	Ep_{lin} = \dfrac{K_s\ x_{m}^2}{2} = \dfrac{\Delta p_{ear} \Delta V_{ear}}{2}
	\label{eq:best_linear_soution}
\end{equation}
Thus, the linear solution can theoretically exploit/store a maximum of $50\%$ from the maximum available hydraulic energy ($\text{max}(E_{hyd})$).

Yet, BRs usually admit non-linear elastic behavior. For example, a BR governed by a Duffing equation is inherently capable of exploiting $65$\% from the same energy source, which is $15$\% better than the best theoretical linear option. Section \ref{sec:SYSTEM MODELING} discusses the details of the modeling and design of the harvester that implements such a non-linear BR as it appeared to be a better solution than the linear approach.

% Figure \ref{fig:OB_vs_LINEAR} shows in blue the hydraulic behavior of the ideal flow rate source previously introduced with the upper limit values of pressure and volume variations.
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{figure}[!htbp]
% 	\centering
% 	\captionsetup{justification=centering}
% 	\includegraphics[trim={22.5cm 0cm 0cm 8.8cm},clip, width=0.35\textwidth]{figures/OB_vs_LINEAR.pdf}
% 	\caption{Hydraulic source exploitation depending on the mechanical load}
% 	\label{fig:OB_vs_LINEAR}
% \end{figure}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
\section{HARVESTER PRESENTATION AND OPERATION \mbox{PRINCIPLE}}
\label{sec:HARVESTER PRESENTATION AND OPERATION PRINCIPLE}
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={3.2cm 0cm 0cm 4.3cm},clip, width=0.7\textwidth]{figures/system_presentation.pdf}
	\caption{Schematic presentation of the frequency-up piezoelectric harvester exploiting the ear canal geometry variation} 
	\label{fig:system_presentation}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The figure \ref{fig:system_presentation} presents a schematic view of the energy harvesting system. It uses a liquid filled earplug to transmit the energy outside the ear canal. To maximize the efficiency, the system integrates a frequency-up conversion stage obtained by a BR. The latter is associated with an amplified piezoelectric generator (APG) \cite{CEDRATTECHNOLOGIES2022} made of a flextensional elastic APX4 steel \cite{AUBERT&DUVAL2022} structure containing stacked lead zirconate titanate (PZT) ceramics (fig. \ref{fig:APG}). The electromechanical converter composed of the BR and the APG theoretically offers higher energy conversion efficiency compared to low frequency solutions and/or flexible electromechanical transducers \cite{Abdelnaby2016}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
\begin{figure}[!htb]
	\begin{center}
		\begin{subfigure}[t]{0.5\linewidth}
			\captionsetup{justification=centering}
			\includegraphics[trim={13cm 0cm 0cm 6cm},clip,width=\linewidth]{figures/APG_schema.pdf}
			\caption{Detailed schema}
			\label{fig:APG_schema}
		\end{subfigure}
		\hfillx
		\begin{subfigure}[t]{0.21\linewidth}
			\captionsetup{justification=centering}
			\includegraphics[trim={29.5cm 0cm 0cm 8cm},clip,width=0.65\linewidth]{figures/APG_photo.pdf}
			\caption{Picture}
			\label{fig:APG_photo}
		\end{subfigure}
		\caption{The APG presentation}
		\label{fig:APG}
	\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

During a mastication cycle, the TMJ compresses the ear canal wall and expels the fluid out of the earplug. The HVs led the fluid alternatively to each HC in order to actuate the BR mass back and forth. The HA adapts the both cylinders stroke to the available earplug swept volume and the actuation force of the BR to the comfort pressure of the ear canal (fig. \ref{fig:system_presentation}).

The BR mass has two stable equilibrium positions, \mbox{$x_m = x_0$ }and \mbox{$x_m = -x_0$}. The harvester operates on two major phases. The first consists on the BR mass actuation, by a HC, from one stable equilibrium position toward the unstable position at $x_m = 0$. During the second phase the mass reaches and oscillates around the opposite stable equilibrium position until it stops, while a portion of the vibration energy is converted into electricity by the GPA. The mass will move backward when the next mastication will occur and complete the harvester cycle.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={20.5cm 0cm 0cm 11.5cm},clip, width=0.8\linewidth]{figures/HV_actuation_detail.pdf}
	\caption{Contact detail between a HV and the BR mass} 
	\label{fig:HV_actuation_detail}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A technological solution for the HV is to use a flexible tube buckled by bending. The figure \ref{fig:HV_actuation_detail} schematizes the integration of such HV around the BR environment. The HV is composed of a flexible tube connected to the hydraulic circuit between a rigid mobile and rigid fixed sheaths. It is in contact with the mass at the T point. The mass motion on the mobile sheath induces a bending angle $\theta$ around the rotational point $O$ located at the buckled section of the flexible tube. Consequently, a pressure loss is generated through the valve in buckled position. The HV is considered closed when the BR mass is at a stable equilibrium position ($x_m=\pm x_0$) and opened when the mass is at $x_m=0$. This last point will be validated experimentally in section \ref{sec:EXPERIMENTAL APPROACH FOR THE HV DESIGN}. Two HVs symmetrically placed on each side of the $\vec{z}$ axis set up an opened hydraulic circuit on one side and a closed one on the other side, depending on the BR mass position. The HV technological choice is motivated by three major arguments. First, the absence of electromechanical transduction compared to a more usual actuated valve minimizes the energy losses for the valve operation. Then, the post-buckling softening effect of the bent tube minimizes the mechanical impact on the BR mass dynamic operation. Finally, it seems well adapted for integration purpose for millimetric application scale.

%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
\section{SYSTEM GLOBAL MODELING}
\label{sec:SYSTEM MODELING}
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
The harvester is a multiphysic system composed of hydraulic, mechanical, and electrical components. This section presents the global multiphysic model describing the system theoretical operation. Two coupled subsystems are considered. The subsection \ref{subsec:The electromechanical converter} shows the modeling of the electromechanical frequency-up converter (BR + APG) under the mechanical influence of a HV and a HC. Subsection \ref{subsec:The hydraulic circuit} discusses the design of the hydraulic circuit composed of the two HVs, the two HCs, the hydraulic amplifier, the pressure separator and the liquid filled earplug.

This work challenges are focused on the experimental validation of the electromechanical converter cycled by two hydraulic valves. In fact several hydraulic miniature solutions are introduced by the literature for both of the components \cite{Wang2020,Xu2021,Zhu2013}. Hence, this section neglects the pressure loss through the pressure separator and the energy loss inside the hydraulic amplifier. These hydraulic components will rather be considered on further work.

@@

The figure \ref{fig:schema_cinematique1} shows the kinematic scheme of the electromechanical converter under the mechanical influence of a HV and a HC. The different rigid bodies are defined in the table \ref{tab:Designation of rigid bodies}. The BR is represented by 4 identical arms articulated by 8 hinges and a central mass. The APG is considered as a spring of stiffness $K$ with an electromechanical coupling $k^2$, standing for the piezoelectric transduction, defined by the equation \ref{eq:k2_def}.\\
The model is based on the following hypotheses:
\begin{itemize}
	\item The only mass considered is the BR mass (2).
	\item All parts are infinitely rigid except for the APG (4).
	\item The hinges are considered elastic: They are defined by their rotational stiffness $K_{\varphi}$
	\item The mechanical damping of the hinges is included in the global viscous damping coefficient $\mu$.
	\item The contact between the BR mass (2) and the HC piston head (5) is considered permanent for $0 < x < x_0$.
	\item \mbox{$x_0 \ll L$}. 
\end{itemize}
\begin{equation}
	k^2 = \dfrac{\alpha^2}{\alpha^2 +  K C_p}
	\label{eq:k2_def}
\end{equation}
%%%%%%%%%%%%%%%%%
\begin{table}[!htbp]
\centering
\resizebox{0.6\linewidth}{!}{%
	\begin{tabular}{ c | c }
		\toprule
		\multicolumn{1}{c}{\textbf{Num}} &
		\multicolumn{1}{c}{\textbf{Name}}                                 \\
		\midrule
		0                                & Fixed frame                    \\
		1                                & BR arm                         \\
		2                                & BR mass                        \\
		3                                & HC piston head                 \\
		4                                & APG                            \\
		5                                & Simplified HV mechanical model \\
		\bottomrule
	\end{tabular}}
\caption{Definition of figure \ref{fig:schema_cinematique1} bodies}
\label{tab:Designation of rigid bodies}
\end{table}
%%%%%%%%%%%%%%%%%%%%%

By isolating the BR mass and using the Newtons 2$^{nd}$ law, we can express its dynamic equilibrium. The projection on the $\vec{x}$ axis of the resulting expression is given by the equation \ref{eq:OB-GPA}. The BR mechanical equilibrium has a mass inertial term, a non-linear stiffness depending on $x_m$, the stiffness of the hinge $K_{\varphi}$ and viscous losses. The first term introduced by the HV is related to its rotational stiffness $K_{HV}$ and the second term is related to the friction losses at the contact point $T$ (fig. \ref{fig:HV_actuation_detail}). $K_{HV}$ and $K_{\varphi}$ both act the same way by making move the stable equilibrium positions of the BR toward $0$ as much as they increase. A dry friction model is chosen to describe the dissipation effect of the contact. The rubbing efforts depend on a dry friction coefficient $f_d$, related to the nature of the material that are rubbing, and the sign of $\dot{x}_m$. The pressure $p_{hc,a}$ induces the HC hydraulic force and the coefficient $\mu_{hc}$ models the viscous friction at the sealing gasket. The hydro-mechanical coupling will be detailed later.

The electrical power generated by the APG is dissipated in a load resistor $R_l$ calculated with an adaptive impedance matching expressed in the equation \ref{eq:R_ch_adaptive_imp} \cite{Liu2013}. 
\begin{equation}
	R_l = \dfrac{1}{C_p w_0}
	\label{eq:R_ch_adaptive_imp}
\end{equation}
Thus, the electrical equation of the APG is :
\begin{equation}
	\dfrac{U_p}{R_l} = 
	-\alpha\dfrac{d}{dt}\biggl(2\sqrt{{l_0}^2-x_m^2}\biggr)
	- C_p\dot{U_p}
	= \frac{2\alpha x_m\dot{x}_m}{\sqrt{L^2+x_m^2}} - C_p\dot{U_p}
\end{equation}
Consequently, the generated power $P_e$ expression is :
\begin{equation}
	P_e = \frac{{U_p}^2}{R_l} 
	\label{eq:P_e}
\end{equation} 
Equation \ref{eq:theta_fonction_de_xm} defines the implicit relation between $\theta$, $x_m$ and the geometrical parameters of the setup. Also, the HV stiffness $K_{HV}$ will depend on its bending angle $\theta$ and the latter will geometrically depend on the BR mass position $x_m$, as showed in figure \ref{fig:HV_actuation_detail}. 
%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htb]
\begin{equation}
 m \ddot{x}_m =-2K(\sqrt{x_m^2+L^2}-l_0)\tan(\varphi) -\mu \dot{x}_m -\frac{4K_{\varphi}\varphi}{L}
				\ -2\alpha U_p \tan(\varphi)
				\ -\dfrac{K_{HV}(x_m)\theta(x_m)}{a} - f_d \text{sign}(\dot{x}_m)
				\  - p_{hc,a}\ S_{hc} - \mu_{c}\ \dot{x}_m
\label{eq:OB-GPA}
\end{equation}
\end{figure*}
% \FloatBarrier
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%

\begin{equation}
\resizebox{.9\linewidth}{!}{$	
x_m = \Biggl[ \dfrac{D_r(1-\cos(\theta))+2a\sin(\theta)}{2\cos(\theta)}\text{,}
				~~ \theta\leq\arctan\biggl(\dfrac{2a}{D_r}\biggr) \Biggr]
				$}
\label{eq:theta_fonction_de_xm}
\end{equation}

>>>>

		BB                       & Buckled beam                                           \\

@@

		GB                       & Guide beam                                             \\

@@

Based on the analysis of the literature, we propose a new solution optimizing the energy conversion efficiency to maximize the harvested energy from the ear canal dynamic motion. The next section states on the hydraulic energy source characterization and on the harvesting strategy that we adopted. Section \ref{sec:HARVESTER PRESENTATION AND OPERATION PRINCIPLE} presents the harvester and describes its operation principle. Section \ref{sec:SYSTEM MODELING} details the global system modeling and section \ref{sec:NUMERICAL MODEL AND SIMULATIONS} presents the numerical simulation of the theoretical behavior of the harvester. Then section \ref{sec:EXPERIMENTAL CHARACTERIZATIONS OF THE ELECTROMECHANICAL CONVERTER} then exposes the experimental validation performed on the electromechanical converter stage and section \ref{sec:EXPERIMENTAL APPROACH FOR THE HV DESIGN} shows the experimental approach for the design of the hydraulic valves for the system cycling. Then, section \ref{sec:MODEL RECALIBRATION WITH EXPERIMENTAL DATA} presents the experimentally adjusted global harvester model and discusses this work major contributions and the harvester potential. Finally, a conclusion is stated.

@@

    %///////////////////////////////////////////// 
	\subsection{Harvesting strategy}	
	\label{The harvesting strategy}
    %/////////////////////////////////////////////
Electromagnetic transducers are usually used to harvest energy from kinetic (vibration) energy sources. The power density of electromagnetic transducers decreases as much as the effective volume of transducing material and the frequency of the energy source decrease \cite{Priya2017,Kulah2008}. Also, the fabrication and the integration of the coil and the moving magnet can come out to be difficult as the gap between the two components has to be carefully managed to prevent non-linear unpredicted responses \cite{Caruntu2001}.

Piezoelectric ceramics appear like good candidates for mechanical energy transduction at small scales, but their high stiffness can limit their use on soft materials as human tissues. Mechanical amplifiers like flextensional structures can nevertheless be used to adapt the stress/displacement levels between the energy source and the transducing stiff material \cite{Abdelnaby2016}. Also, the best energy conversion efficiency for piezoelectric ceramics is achieved for at the transducer resonance. As the mean mastication frequency is estimated to \mbox{$1.57$Hz}, the harvesting system could benefit from a frequency-up conversion stage \cite{Ashraf2011,Peng2021} to increase the frequency of the energy source and so the energy conversion efficiency of the transducer. A majority of the frequency-up systems with piezoelectric transducers use mechanical stops with piezoelectric ceramic cantilevers to reach high frequencies with a good mechanical coupling \cite{Edwards2013,Gu2011,Lee2007}. Stoppers however dissipate energy. Alternative solutions use mechanically bistable resonators (BR) \cite{Vocca2012}. Recent works led to the development and optimization of bistable structures integrating stacked piezoelectric ceramics inside flextensional elastic structures \cite{Huguet2017}. They show enhanced performances due to high electromechanical coupling. The electromechanical converter, composed of a BR with piezoelectric ceramics in a flextensional structure, theoretically offers higher energy conversion efficiency compared to low frequency solutions and/or flexible electromechanical transducers \cite{Abdelnaby2016,Peng2021}.

The hydraulic-mechanic interface can be a hydraulic cylinder (HC). It can store the energy in the frequency-up converter by actuating it at the frequency of human mastication. The amount of extractable energy from the hydraulic source will then depend on the mechanical stage behavior. Before being converted in electricity, the energy is in fact stored in a mechanical potential reservoir. During the low frequency actuation, the forces applied on each side of the HC piston are equal. Equation \ref{eq:hydraulic-mechanic_interface} models the hydraulic-mechanic interface with $x_{m}$ and $ S_{hc}$ being respectively the dynamic mass position on the $\vec{x}$ axis and the HC internal section.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={19.7cm 0cm 0cm 13cm},clip, width=0.7\linewidth]{figures/hydraulic_mechanic_interface.pdf}
	\caption{Hydraulic source exploitation depending on the mechanical load}
	\label{fig:hydraulic_mechanic_interface}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Therefore, the potential energy stored in a linear resonator from the ideal hydraulic source previously described can be expressed as follows :
\begin{equation}
	Ep_{lin} = \dfrac{K_s\ x_{m}^2}{2} = \dfrac{\Delta p_{ear} \Delta V_{ear}}{2}
	\label{eq:best_linear_soution}
\end{equation}
Thus, the linear solution can theoretically exploit/store a maximum of $50\%$ from the maximum available hydraulic energy ($\text{max}(E_{hyd})$).

Non-linear elastic potential reservoirs can also be considered. This work presents the energy extraction capability of a BR governed by a Duffing equation. It admits 2 stable equilibrium positions \mbox{$x_m=\pm x_0$}, an unstable one in \mbox{$x_m=0$} and its stiffness depends on its structural buckling level $\epsilon$ defined later in equation \ref{eq:epsilon_def}. The maximum theoretical energy in the BR for a quasi-static actuation is equal to the height of the potential energy barrier $E_{pb}$ when the mass position varies from \mbox{$x_m=\pm x_0$} to \mbox{$x_m=0$} (eq. \ref{eq:Ep_bar}). It will be a fraction $n$ of the upper limit of the available hydraulic energy (eq. \ref{eq:max_hydraulic_energy}) where $n$ has to be maximized. 
\begin{equation}
	E_{pb} = \dfrac{K x_0^2\epsilon^2}{3} = n(p_c \cdot (\Delta V_{ear})_{max})
	\label{eq:Ep_bar}
\end{equation}
We see later that it is inherently capable of exploiting $65$\% from the hydraulic energy source, which is $15$\% better than the best theoretical linear option. Section \ref{sec:SYSTEM MODELING} discusses the details of the modeling and design of the harvester that implements such a non-linear BR as it appeared to be a better solution than the linear approach. 
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
\section{HARVESTER PRESENTATION AND OPERATION \mbox{PRINCIPLE}}
\label{sec:HARVESTER PRESENTATION AND OPERATION PRINCIPLE}
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={3.2cm 0cm 0cm 4.3cm},clip, width=0.7\textwidth]{figures/system_presentation.pdf}
	\caption{Schematic presentation of the frequency-up piezoelectric harvester exploiting the ear canal geometry variation} 
	\label{fig:system_presentation}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The figure \ref{fig:system_presentation} presents a schematic view of the energy harvesting system. It uses a liquid filled earplug to transmit the energy outside the ear canal. To maximize the efficiency, the system integrates a frequency-up conversion stage obtained by a BR. The latter is associated with an amplified piezoelectric generator (APG) \cite{CEDRATTECHNOLOGIES2022} made of a flextensional elastic APX4 steel \cite{AUBERT&DUVAL2022} structure containing stacked lead zirconate titanate (PZT) ceramics (fig. \ref{fig:APG}).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
\begin{figure}[!htb]
	\begin{center}
		\begin{subfigure}[t]{0.5\linewidth}
			\captionsetup{justification=centering}
			\includegraphics[trim={13cm 0cm 0cm 6cm},clip,width=\linewidth]{figures/APG_schema.pdf}
			\caption{Detailed schema}
			\label{fig:APG_schema}
		\end{subfigure}
		\hfillx
		\begin{subfigure}[t]{0.21\linewidth}
			\captionsetup{justification=centering}
			\includegraphics[trim={29.5cm 0cm 0cm 8cm},clip,width=0.65\linewidth]{figures/APG_photo.pdf}
			\caption{Picture}
			\label{fig:APG_photo}
		\end{subfigure}
		\caption{The APG presentation}
		\label{fig:APG}
	\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

During a mastication cycle, the TMJ compresses the ear canal wall and expels the fluid out of the earplug. The HVs led the fluid alternatively to each HC in order to actuate the BR mass back and forth. The HA adapts both the cylinders stroke to the available earplug swept volume and the actuation force of the BR to the comfort pressure of the ear canal (fig. \ref{fig:system_presentation}).

The BR mass has two stable equilibrium positions, \mbox{$x_m = x_0$ }and \mbox{$-x_0$}. The harvester operates on two major phases. The first consists on the BR mass actuation, by a HC, from one stable equilibrium position toward the unstable position at $x_m = 0$. During the second phase the mass reaches and oscillates around the opposite stable equilibrium position until it stops, while a portion of the vibration energy is converted into electricity by the GPA. The mass will move backward when the next mastication will occur and complete the harvester cycle.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={20.5cm 0cm 0cm 11.5cm},clip, width=0.8\linewidth]{figures/HV_actuation_detail.pdf}
	\caption{Contact detail between a HV and the BR mass} 
	\label{fig:HV_actuation_detail}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A technological solution for the HV is to use a flexible tube buckled by bending. The figure \ref{fig:HV_actuation_detail} schematizes the integration of such a HV around the BR environment. The HV is composed of a flexible tube connected to the hydraulic circuit between a rigid mobile and rigid fixed sheaths. It is in contact with the mass at the T point. The mass motion on the mobile sheath induces a bending angle $\theta$ around the rotational point $O$ located at the buckled section of the flexible tube. Consequently, a pressure loss is generated through the valve in buckled position. The HV is to be closed when the BR mass is at a stable equilibrium position ($x_m=\pm x_0$) and opened when the mass is at $x_m=0$. This last point will be validated experimentally in section \ref{sec:EXPERIMENTAL APPROACH FOR THE HV DESIGN}. Two HVs symmetrically placed on each side of the $\vec{z}$ axis set up an opened hydraulic circuit on one side and a closed one on the other side, depending on the BR mass position. The HV technological choice is motivated by three major arguments. First, the absence of dedicated electromechanical transduction compared to a more usual actuated valve minimizes the energy losses for the valve operation. Then, the post-buckling softening effect of the bent tube minimizes the mechanical impact on the BR mass dynamic operation. Finally, it seems well adapted for integration purpose for millimetric application scale.

%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
\section{SYSTEM GLOBAL MODELING}
\label{sec:SYSTEM MODELING}
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
This section presents the global multiphysic model describing the system operation. Two coupled subsystems are considered. The subsection \ref{subsec:The electromechanical converter} shows the modeling of the electromechanical frequency-up converter (BR + APG) under the mechanical influence of a HV and a HC. Subsection \ref{subsec:The hydraulic circuit} discusses the design of the hydraulic circuit composed of the two HVs, the two HCs, the hydraulic amplifier and the liquid filled earplug.

This work challenges are focused on the experimental validation of the electromechanical converter cycled by two hydraulic valves. In fact several hydraulic miniature solutions are introduced by the literature for both of the components \cite{Wang2020,Xu2021,Zhu2013}. Hence, this section neglects the pressure loss through the pressure separator and the energy loss inside the hydraulic amplifier. These hydraulic components will rather be considered for further work.

@@

The figure \ref{fig:schema_cinematique1} shows the kinematic scheme of the electromechanical converter under the mechanical influence of a HV and a HC. The rigid bodies are defined in the table \ref{tab:Designation of rigid bodies}. The BR is represented by 4 identical arms articulated by 8 hinges and a central mass. The APG is considered as a spring of stiffness $K$ with an electromechanical coupling $k^2$, standing for the piezoelectric transduction and defined by the equation \ref{eq:k2_def}.\\
The model is based on the following hypotheses:
\begin{itemize}
	\item The only mass considered is the BR mass (2).
	\item All parts are rigid except for the APG (4).
	\item The hinges are considered elastic: They are defined by their rotational stiffness $K_{\varphi}$
	\item The mechanical damping of the hinges is included in the global viscous damping coefficient $\mu$.
	\item The contact between the BR mass (2) and the HC piston head (5) is considered permanent for $0 < x < x_0$.
	\item \mbox{$x_0 \ll L$}. 
\end{itemize}
\begin{equation}
	k^2 = \dfrac{\alpha^2}{\alpha^2 +  K C_p}
	\label{eq:k2_def}
\end{equation}
%%%%%%%%%%%%%%%%%
\begin{table}[!htbp]
\centering
\resizebox{0.6\linewidth}{!}{%
	\begin{tabular}{ c | c }
		\toprule
		\multicolumn{1}{c}{\textbf{Num}} &
		\multicolumn{1}{c}{\textbf{Name}}                                 \\
		\midrule
		0                                & Fixed frame                    \\
		1                                & BR arm                         \\
		2                                & BR mass                        \\
		3                                & HC piston head                 \\
		4                                & APG                            \\
		5                                & Simplified HV mechanical model \\
		\bottomrule
	\end{tabular}}
\caption{Definition of figure \ref{fig:schema_cinematique1} bodies}
\label{tab:Designation of rigid bodies}
\end{table}
%%%%%%%%%%%%%%%%%%%%%

By isolating the BR mass and using the Newtons 2$^{nd}$ law, we can express its dynamic equilibrium. The projection on the $\vec{x}$ axis of the resulting expression is given by the equation \ref{eq:OB-GPA}. The BR mechanical equilibrium has a mass inertial term, a non-linear stiffness depending on $x_m$, the stiffness of the hinge $K_{\varphi}$ and viscous losses. The first term introduced by the HV is related to its rotational stiffness $K_{HV}$ and the second term is related to the friction losses at the contact point $T$ (fig. \ref{fig:HV_actuation_detail}). $K_{HV}$ and $K_{\varphi}$ both act the same way by shifting the stable equilibrium positions of the BR toward $0$ as much as they increase. A dry friction model is chosen to describe the dissipation effect of the contact. The rubbing efforts depend on a dry friction coefficient $f_d$, related to the nature of the material that are rubbing, and the sign of $\dot{x}_m$. The coefficient $\mu_{hc}$ models the viscous friction at the sealing gasket of the HC. The hydro-mechanical coupling will be detailed later.
